Transformation of forecasts for evaluating predictive performance in an epidemiological context

### 2023-01-09 main.tex
update manuscript, remove a few passages

\title{Transformation of forecasts for evaluating predictive performance in an epidemiological context}
  \author{Nikos I. Bosse\thanks{Department of Infectious Disease Epidemiology, London School of Hygiene \& Tropical Medicine, London, United Kingdom} $^{,}$\thanks{Centre for the Mathematical Modelling of Infectious Diseases, London, United Kingdom} $^{,*}$, 
  Sam Abbott\footnotemark[1] $^{,}$\footnotemark[2]$ ^{}$, 
  Anne Cori\thanks{MRC Centre for Outbreak Analysis and Modelling, Department of Infectious Disease Epidemiology, School of Public Health, Imperial College London, London, United Kingdom} $^{}$, \\
  Edwin van Leeuwen\thanks{Department of Infectious Disease Epidemiology, London School of Hygiene \& Tropical Medicine, London, United Kingdom} $^{,}$\thanks{UK Health Security Agency, London, United Kingdom} $^{}$, 
  Johannes Bracher\thanks{Institute of Economic Theory and Statistics, Karlsruhe Institute of Technology, Karlsruhe, Germany} $^{}$, 
  Sebastian Funk\footnotemark[1] $^{,}$\footnotemark[2]$ ^{}$}

\maketitle
%\tableofcontents
\begin{abstract}
Forecast evaluation plays an essential role in improving forecasting models can help inform future decision making. In epidemiology, probabilistic forecasts are often scored using the Weighted Interval Score (WIS) or the Continuous Ranked Probability Score (CRPS), which are a measure of absolute distance between forecast and observation. Infectious disease transmission is commonly conceptualised as a non-stationary processes in terms of the growth rate or the effective reproduction number. Scoring based on the absolute distance between forecast and observation may not reflect this underlying modelling task well and may make it difficult to compare forecasts across time, space, and different forecast targets. As a solution, we propose transforming the data before scoring the forecasts to better reflect our understanding of the generative process. Depending on the context, many transformations may be appropriate. We describe the log-transformation as one specific example in detail and discuss its interpretation as a measure of relative error and as a score for an implicit forecast of the exponential growth rate. Applying the log-transformation to data from the European COVID-19 Forecast Hub, we found that it changed model rankings, regardless of stratification by forecast date, location or target types, and emphasised situations in which models missed lower inflection points and consequent rises in numbers, while penalising missed peaks less severely. 
\end{abstract}

@@

Probabilistic forecasts \citep{heldProbabilisticForecastingInfectious2017} play an important role in decision-making in epidemiology and public health \citep{reichCollaborativeMultiyearMultimodel2019, funkShorttermForecastsInform2020, cramerEvaluationIndividualEnsemble2021, bracherShorttermForecastingCOVID192021, europeancovid-19forecasthubEuropeanCovid19Forecast2021, sherrattPredictivePerformanceMultimodel2022}, as well as other areas as diverse as economics \citep{timmermannForecastingMethodsFinance2018, elliottForecastingEconomicsFinance2016} or meteorology \citep{gneitingWeatherForecastingEnsemble2005, kukkonenReviewOperationalRegionalscale2012}. Epidemiological modelling in particular has received widespread attention during the COVID-19 pandemic. Evaluations of forecasts can provide feedback for forecasters and researchers to improve their models and train ensembles, and help decision makers distinguish good from bad predictions and choosing forecasters and models that should inform future decisions.

Probabilistic forecasts are usually evaluated using so-called proper scoring rules \citep{gneitingStrictlyProperScoring2007}, which return a numerical score as a function of the forecast and the observed data. Proper scoring rules are constructed such that forecasters are incentivised to report their true belief about the future. Examples of proper scoring rules that have been used to assess epidemiological forecasts are the Continuous Ranked Probability Score~\citep[CRPS,][]{gneitingStrictlyProperScoring2007} or its discrete equivalent, the Ranked Probability Score~\citep[RPS,][]{funkAssessingPerformanceRealtime2019}, and the Weighted Interval Score \citep{bracherEvaluatingEpidemicForecasts2021}. 
The CRPS measures the distance of the predictive distribution to the observed data as 
\begin{linenomath*}
\begin{equation*}
    \text{CRPS}(F, y) = \int_{-\infty}^\infty \left( F(x) - 1(x \geq y) \right)^2 dx,
\end{equation*}    
\end{linenomath*}
where $y$ is the true observed value and $F$ the cumulative distribution function (CDF) of the predictive distribution. The CRPS can be understood as a generalisation of the absolute error to predictive distributions. The WIS is an approximation of the CRPS for predictive distributions represented by a set of predictive quantiles and is currently used to assess forecasts in COVID-19 forecast hubs in the US \citep{cramerCOVID19ForecastHub2020, cramerEvaluationIndividualEnsemble2021}, Europe \citep{sherrattPredictivePerformanceMultimodel2022}, Germany and Poland \citep{bracherShorttermForecastingCOVID192021, bracherNationalSubnationalShortterm2021}, as well as the US Influenza Forecasting Hub \citep{CdcepiFlusightforecastdata2022}. The WIS is defined as 
\begin{linenomath*}
\begin{equation*}
    \text{WIS}(F, y) = \frac{1}{K} \times \sum_{k = 1}^{K} 2 \times \left[ \boldsymbol{1}(y \leq q_{\tau_k}) - \tau_k \right] \times ( q_{\tau_k} - y), 
\end{equation*}
\end{linenomath*}
where $q_{\tau}$ is the $\tau$ quantile of the forecast $F$, $y$ is the observed outcome, $K$ is the number of predictive quantiles provided and $\boldsymbol{1}$ is the indicator function. We show an alternative definition based on central prediction intervals in Section \ref{sec:alternative-wis}.

@@

The remainder of the article is structured as follows. In Sections \ref{sec:methods:relative}--\ref{sec:methods:vst} we provide some mathematical intuition on applying the log transformation prior to evaluating the CRPS, highlighting the connections to relative error measures, the epidmemic growth rate and variance stabilizing transformations.
%We first provide a mathematical intuition of the impact of the log-transformation and its interpretation as relative error (Section \ref{sec:methods:relative}, measure of the accuracy of a forecast of the growth rate (Section \ref{sec:methods:growthrate}) and it's effect as a variance-stabilising transformation that makes can make scores independent of the mean of the forecast target (Section \ref{sec:methods:vst}. 
We then discuss the effect of the transformation on forecast rankings (section \ref{sec:methods:rankings} and discuss some practical considerations relevant for applying transformations in general and the log-transformation in particular (Section \ref{sec:methods:considerations}). We illustrate the effect of the log-transformation using forecasts submitted to the European COVID-19 Forecast Hub  \citep{europeancovid-19forecasthubEuropeanCovid19Forecast2021, sherrattPredictivePerformanceMultimodel2022} (Section \ref{sec:results}). Finally, we provide scoring recommendations, discuss alternative transformations that may be useful in different contexts, and suggest further research avenues on the use of transformed scores in the evaluation of infectious disease forecasts (Section \ref{sec:discussion}).

@@

\subsection{Effects on model rankings}
\label{sec:methods:rankings}
Rankings between different forecasters based on the CRPS may change when making use of a transformation both when looking at aggregate scores as well as when looking at a single forecast. We illustrate this in Figure \ref{fig:illustration-ranking} with two forecasters, A and B, issuing two different distributions with different dispersion. When showing the obtained CRPS as a function of the observed value, it can be seen that the ranking between the two forecasters may change when scoring the forecast on the logarithmic, rather than the natural scale. In particular, on the natural scale, forecaster A, who issues a more uncertain distribution, receives a better score than forecaster B for observed values far away from the centre of the respective predictive distribution. On the log scale, however, forecaster A receives a lower score for large observed values, being more heavily penalised for assigning large probability to small values (which, in relative terms, are far away from the actual observation).

@@

Overall model rankings would be expected to differ even more when scores are averaged across multiple forecasts or targets. The change in rankings of aggregate scores is not mainly driven by the kinds of changes in model rankings for single forecasts just discussed. Rather, average scores will be most influenced by the order of magnitude of scores for different forecast targets across time, location and target type. On the natural scale, large observations will account for the majority of the overall score but will not dominate average CRPS values obtained after log transformation in the same way. Depending on the relationship between mean and variance of the forecast target, a log-transformation, however, may also lead to systematically larger scores assigned to small forecast targets, as illustrated in Figure \ref{fig:SIM-wis-state-size-mean}. A different transformation like the square-root may then be appropriate to stabilise the variance effectively and make scores independent of the mean of the target quantity.

@@

In practice, one issue with transformations, such as the log transform, is that they may not be readily applicable to negative numbers or zero values, which need to be removed or handled otherwise. Small discrete values can pose an additional problem as it may be difficult to reliably evaluate relative errors. 
One common approach is to add a small quantity, such as 1, to all observations and predictions before taking the logarithm. This represents a strictly monotonic transformation and therefore still preserves the propriety of the resulting score. The choice of the number to add influences scores and rankings, as measures of relative errors shrink when adding a constant to the forecast and the observation. Adding a number to the forecasts and observations changes scores for forecasts of small quantities most, as relative errors shrink more the smaller the original value before adding a constant. In principle, it would also be possible to exploit the difference in how scores are affected in order to equalise scores for forecasts of quantities across different scales by adding a larger number (e.g. 100 or 10,000) if average scores are dominated too strongly by forecasts for small quantities.

@@

As an empirical comparison of evaluating forecasts on the natural and on the log scale, we use forecasts from the European Forecast Hub \citep{europeancovid-19forecasthubEuropeanCovid19Forecast2021, sherrattPredictivePerformanceMultimodel2022}. 
The European COVID-19 Forecast Hub is one of several COVID-19 Forecast hubs\citep{cramerEvaluationIndividualEnsemble2021, bracherShorttermForecastingCOVID192021} which have been systematically collecting, aggregating and evaluating forecasts of several COVID-19 targets created by different teams every week. Forecasts are made one to four weeks ahead into the future and follow a quantile-based format with a set of 22 quantiles plus the median ($0.01, 0.025, 0.05, ..., 0.5, ... 0.95, 0.975, 0.99$).

@@

As expected on the natural scale, scores correlate strongly with the magnitude of the median forecast (Spearman rank correlation: 0.9 and 0.92) (see Figure\ref{fig:HUB-mean-locations}A, B). We report the Spearman rank correlation here, rather than the Pearson correlation, as it tends to be more robust and is invariant to transformations. 
For scores on the log scale, the correlation is weaker and slightly negative (Spearman correlation: -0.35 and -0.55), implying a tendency towards larger scores for forecasts of smaller quantities.

@@

The rank order of different forecasting models (see Figure \ref{fig:HUB-rank-order} indicates that models that do not make use of a exponential error model and thus would be biased towards under-prediction during periods of exponential growth, such as the MUNI-ARMA model, were ranked lower when using a log-transform. The epiforecasts-EpiNow2 forecast model, on the other hand~(created by co-authors of this study), which makes forecasts based on the behaviour of the reproduction number and thus implicitly uses an exponential error model, was the most impacted by the change to log-scale scoring moving from last place for reported cases to 4th place. Other models that are based on modelling the growth rate, such as the LANL-GrowthRate forecaster, do less well after a log-transform, indicating that this potential association between model structure and score under different approximations does not hold strictly. Encouragingly for the European Forecast Hub, the Hub ensemble, which is the forecast the organisers suggest forecast consumers make use of, remains one of the top forecasts across scoring schemes and indeed ranks higher for reported cases when a log-transform is used.

@@

In this paper we proposed the use of transformations, with a particular focus on the log transformation, in order to address issues that arise when evaluating epidemiological forecasts based on measures of absolute error and their probabilistic generalisations (i.e CRPS and WIS). We gave a mathematical intuition for the log transformation and showed that scores on the log scale can be interpreted as a) a measure of relative prediction errors, as well as b) a score for a forecast of the exponential growth rate of the target quantity and c) as variance stabilising transformation in some settings.
When applying this approach to forecasts from the European COVID-19 Forecast Hub, we found overall scores on the log scale to be more equal across, time, location and target type (cases, deaths) than scores on the natural scale. Scores on the log scale were much less influenced by the overall incidence level in a country, and showed a slight tendency to be higher in locations with very low incidences. We found that model rankings changed noticeably, favouring models like epiforecasts-EpiNow2 which uses a log scale generative process and a negative binomial observation model, and disfavouring models like MUNI-ARIMA which uses a square root transform to stabilise variance. On the natural scale, missing the peak and overshooting was more severely penalised than missing the nadir and the following upswing in numbers. Both failure modes tended to be more equally penalised on the log scale (with undershooting receiving slightly higher penalties in our example).

>>>>

\title{Transformation of forecasts for evaluating predictive performance in an epidemiological context}
  \author{Nikos I. Bosse\thanks{Department of Infectious Disease Epidemiology, London School of Hygiene \& Tropical Medicine, London, United Kingdom} $^{,}$\thanks{Centre for the Mathematical Modelling of Infectious Diseases, London, United Kingdom} $^{,*}$, 
  Sam Abbott\footnotemark[1] $^{,}$\footnotemark[2]$ ^{}$, 
  Anne Cori\thanks{MRC Centre for Outbreak Analysis and Modelling, Department of Infectious Disease Epidemiology, School of Public Health, Imperial College London, London, United Kingdom} $^{}$, \\
  Edwin van Leeuwen\thanks{Department of Infectious Disease Epidemiology, London School of Hygiene \& Tropical Medicine, London, United Kingdom} $^{,}$\thanks{UK Health Security Agency, London, United Kingdom} $^{}$, 
  Johannes Bracher\thanks{Chair of Statistical Methods and Econometrics, Karlsruhe Institute of Technology, Karlsruhe, Germany} $^{}$, 
  Sebastian Funk\footnotemark[1] $^{,}$\footnotemark[2]$ ^{}$}

\maketitle
%\tableofcontents
\begin{abstract}
Forecast evaluation plays an essential role in improving forecasting models and can help inform future decision making. In epidemiology, probabilistic forecasts are often scored using the Weighted Interval Score (WIS) or the Continuous Ranked Probability Score (CRPS), which are a measure of absolute distance between forecast and observation. Infectious disease transmission is commonly conceptualised as a non-stationary processes in terms of the growth rate or the effective reproduction number. Scoring based on the absolute distance between forecast and observation may not reflect this underlying modelling task well and may make it difficult to compare forecasts across time, space, and different forecast targets. As a solution, we propose transforming the data before scoring the forecasts to better reflect our understanding of the generative process. Depending on the context, many transformations may be appropriate. We describe the log-transformation as one specific example in detail and discuss its interpretation as a measure of relative error and as a score for an implicit forecast of the exponential growth rate. Applying the log-transformation to data from the European COVID-19 Forecast Hub, we found that it changed model rankings, regardless of stratification by forecast date, location or target types, and emphasised situations in which models missed lower inflection points and consequent rises in numbers, while penalising missed peaks less severely. 
\end{abstract}

% Suggestion J:
% Forecast evaluation plays an essential role in the development cycle of pedictive epidemic models and can inform their use for public health decision making. Common scores to evaluate epidemiological forecasts are the Continuous Ranked Probability Score (CRPS) and the Weighted Interval Score (WIS), which are both measures of the absolute distance between the forecast distribution and the observation. They are commonly applied directly to predicted and observed incidence counts, but it can be questioned whether this yields the most meaningful results given the exponential nature of epidemic processes and the fact that observed values over space and time can span several orders of magnitude. In this paper we argue that applying the CRPS to incidence counts on a logarithmic rather than natural scale effectively mitigates these difficulties, yielding epidemiologically meaningful and easily interpretable results. We motivate the procedure threefold: firstly, it can be interpreted as a probabilistic version of a relative error. Secondly, it reflects how well models predicted the time-varying epidemic growth rate. And lastly, using arguments on variance-stabilizing transformations, it can be shown that under the assumption of a quadratic mean-variance relationship, the logarithmic transformation leads to expected CRPS values which are independent of the order of magnitude of the predicted quantity. This implies that different forecasting tasks will will have a similar impact on overall evaluation results. Applying the log-transformation to data from the European COVID-19 Forecast Hub, we find that it changes model rankings, regardless of stratification by forecast date, location or target types. Situations in which models missed beginning upward swings are more strongly emphasized, while penalising missed peaks are less severely penalized. Also, we show that the assumption of a quadratic mean-variance relationship is quite closely aligned with empirical patterns.

@@

Probabilistic forecasts \citep{heldProbabilisticForecastingInfectious2017} play an important role in decision-making in epidemiology and public health \citep{reichCollaborativeMultiyearMultimodel2019, funkShorttermForecastsInform2020, cramerEvaluationIndividualEnsemble2021, bracherShorttermForecastingCOVID192021, europeancovid-19forecasthubEuropeanCovid19Forecast2021, sherrattPredictivePerformanceMultimodel2022}, as well as other areas as diverse as economics \citep{timmermannForecastingMethodsFinance2018, elliottForecastingEconomicsFinance2016} or meteorology \citep{gneitingWeatherForecastingEnsemble2005, kukkonenReviewOperationalRegionalscale2012}. Epidemiological modelling in particular has received widespread attention during the COVID-19 pandemic. Evaluations of forecasts can provide feedback for forecasters and researchers to improve their models and train ensembles. It moreover helps decision makers distinguish good from bad predictions and choose forecasters and models that should inform future decisions.

Probabilistic forecasts are usually evaluated using so-called proper scoring rules \citep{gneitingStrictlyProperScoring2007}, which return a numerical score as a function of the forecast and the observed data. Proper scoring rules are constructed such that forecasters are incentivised to report their true belief about the future. Examples of proper scoring rules that have been used to assess epidemiological forecasts are the Continuous Ranked Probability Score~\citep[CRPS,][]{gneitingStrictlyProperScoring2007} or its discrete equivalent, the Ranked Probability Score~\citep[RPS,][]{funkAssessingPerformanceRealtime2019}, and the Weighted Interval Score \citep{bracherEvaluatingEpidemicForecasts2021}. 
The CRPS measures the distance of the predictive distribution to the observed data as 
\begin{linenomath*}
\begin{equation*}
    \text{CRPS}(F, y) = \int_{-\infty}^\infty \left( F(x) - 1(x \geq y) \right)^2 dx,
\end{equation*}    
\end{linenomath*}
where $y$ is the true observed value and $F$ the cumulative distribution function (CDF) of the predictive distribution. The CRPS can be understood as a generalisation of the absolute error to predictive distributions, and interpreted n the natural scale of the data. The WIS is an approximation of the CRPS for predictive distributions represented by a set of predictive quantiles and is currently used to assess forecasts in COVID-19 forecast hubs in the US \citep{cramerCOVID19ForecastHub2020, cramerEvaluationIndividualEnsemble2021}, Europe \citep{sherrattPredictivePerformanceMultimodel2022}, Germany and Poland \citep{bracherShorttermForecastingCOVID192021, bracherNationalSubnationalShortterm2021}, as well as the US Influenza Forecasting Hub \citep{CdcepiFlusightforecastdata2022}. The WIS is defined as 
\begin{linenomath*}
\begin{equation*}
    \text{WIS}(F, y) = \frac{1}{K} \times \sum_{k = 1}^{K} 2 \times \left[ \boldsymbol{1}(y \leq q_{\tau_k}) - \tau_k \right] \times ( q_{\tau_k} - y), 
\end{equation*}
\end{linenomath*}
where $q_{\tau}$ is the $\tau$ quantile of the forecast $F$, $y$ is the observed outcome, $K$ is the number of predictive quantiles provided and $\boldsymbol{1}$ is the indicator function. We show an alternative definition based on central prediction intervals in Section \ref{sec:alternative-wis}.

@@

The remainder of the article is structured as follows. In Sections \ref{sec:methods:relative}--\ref{sec:methods:vst} we provide some mathematical intuition on applying the log transformation prior to evaluating the CRPS, highlighting the connections to relative error measures, the epidemic growth rate and variance stabilizing transformations.
%We first provide a mathematical intuition of the impact of the log-transformation and its interpretation as relative error (Section \ref{sec:methods:relative}, measure of the accuracy of a forecast of the growth rate (Section \ref{sec:methods:growthrate}) and it's effect as a variance-stabilising transformation that makes can make scores independent of the mean of the forecast target (Section \ref{sec:methods:vst}. 
We then discuss the effect of the transformation on forecast rankings (section \ref{sec:methods:rankings} and discuss some practical considerations relevant for applying transformations in general and the log-transformation in particular (Section \ref{sec:methods:considerations}). We illustrate the effect of the log-transformation using forecasts submitted to the European COVID-19 Forecast Hub  \citep{europeancovid-19forecasthubEuropeanCovid19Forecast2021, sherrattPredictivePerformanceMultimodel2022} (Section \ref{sec:results}). Finally, we provide scoring recommendations, discuss alternative transformations that may be useful in different contexts, and suggest further research avenues on the use of transformed scores in the evaluation of infectious disease forecasts (Section \ref{sec:discussion}).

@@

\subsection{Effects on model rankings}
\label{sec:methods:rankings}
Rankings between different forecasters based on the CRPS may change when making use of a transformation, both in terms of aggregate and individual scores. We illustrate this in Figure \ref{fig:illustration-ranking} with two forecasters, A and B, issuing two different distributions with different dispersion. When showing the obtained CRPS as a function of the observed value, it can be seen that the ranking between the two forecasters may change when scoring the forecast on the logarithmic, rather than the natural scale. In particular, on the natural scale, forecaster A, who issues a more uncertain distribution, receives a better score than forecaster B for observed values far away from the centre of the respective predictive distribution. On the log scale, however, forecaster A receives a lower score for large observed values, being more heavily penalised for assigning large probability to small values (which, in relative terms, are far away from the actual observation).

@@

Overall model rankings would be expected to differ even more when scores are averaged across multiple forecasts or targets. The change in rankings of aggregate scores is not mainly driven by the kinds of changes in model rankings for single forecasts just discussed. Rather, average scores will be most influenced by the order of magnitude of scores for different forecast targets across time, location and target type. Large observations will dominate average CRPS values when evaluation is done on the natural scale, but much less so after log transformation. Depending on the relationship between mean and variance of the forecast target, a log-transformation may even lead to systematically larger scores assigned to small forecast targets, as illustrated in Figure \ref{fig:SIM-wis-state-size-mean}. A different transformation like the square-root may then be more appropriate to make scores independent of the mean of the target quantity.

@@

In practice, one issue with transformations, such as the log transform, is that they are not readily applicable to negative numbers or zero values, which need to be removed or handled otherwise. Small discrete values can pose an additional problem as it may be difficult to reliably evaluate relative errors. 
One common approach is to add a small quantity, such as 1, to all observations and predictions before taking the logarithm. This represents a strictly monotonic transformation and therefore still preserves the propriety of the resulting score. The choice of the number to add influences scores and rankings, as measures of relative errors shrink when adding a constant to the forecast and the observation. Adding a number to the forecasts and observations changes scores for forecasts of small quantities most, as relative errors shrink more the smaller the original value before adding a constant. In principle, it would also be possible to exploit the difference in how scores are affected in order to equalise scores for forecasts of quantities across different scales by adding a larger number (e.g. 100 or 10,000) if average scores are dominated too strongly by forecasts for small quantities.

@@

As an empirical comparison of evaluating forecasts on the natural and on the log scale, we use forecasts from the European Forecast Hub \citep{europeancovid-19forecasthubEuropeanCovid19Forecast2021, sherrattPredictivePerformanceMultimodel2022}. 
The European COVID-19 Forecast Hub is one of several COVID-19 Forecast hubs \citep{cramerEvaluationIndividualEnsemble2021, bracherShorttermForecastingCOVID192021} which have been systematically collecting, aggregating and evaluating forecasts of several COVID-19 targets created by different teams every week. Forecasts are made one to four weeks ahead into the future and follow a quantile-based format with a set of 22 quantiles plus the median ($0.01, 0.025, 0.05, ..., 0.5, ... 0.95, 0.975, 0.99$).

@@

As expected, on the natural scale, scores correlate strongly with the magnitude of the median forecast (Spearman rank correlation: 0.9 and 0.92) (see Figure\ref{fig:HUB-mean-locations}A, B). We report the Spearman rank correlation here, rather than the Pearson correlation, as it tends to be more robust and is invariant to transformations. 
For scores on the log scale, the correlation is weaker and slightly negative (Spearman correlation: -0.35 and -0.55), implying a tendency towards larger scores for forecasts of smaller quantities.

@@

The rank order of different forecasting models changes noticeable (see Figure \ref{fig:HUB-rank-order}. 
% I removed this part as it doesn't seem accurate anymore / we don't even have all the models in there anymore. 
%indicates that models that do not make use of a exponential error model and thus would be biased towards under-prediction during periods of exponential growth, such as the MUNI-ARMA model, were ranked lower when using a log-transform. The epiforecasts-EpiNow2 forecast model, on the other hand~(created by co-authors of this study), which makes forecasts based on the behaviour of the reproduction number and thus implicitly uses an exponential error model, was the most impacted by the change to log-scale scoring moving from last place for reported cases to 4th place. Other models that are based on modelling the growth rate, such as the LANL-GrowthRate forecaster, do less well after a log-transform, indicating that this potential association between model structure and score under different approximations does not hold strictly.
Encouragingly for the European Forecast Hub, the Hub ensemble, which is the forecast the organisers suggest forecast consumers make use of, remains one of the top forecasts across scoring schemes and indeed ranks higher for reported cases when a log-transform is used.

@@

In this paper we proposed the use of transformations, with a particular focus on the log transformation, in order to address issues that arise when evaluating epidemiological forecasts based on measures of absolute error and their probabilistic generalisations (i.e CRPS and WIS). We gave a mathematical intuition for the log transformation and showed that scores on the log scale can be interpreted as a) a measure of relative prediction errors, as well as b) a score for a forecast of the exponential growth rate of the target quantity and c) as variance stabilising transformation in some settings.
When applying this approach to forecasts from the European COVID-19 Forecast Hub, we found overall scores on the log scale to be more equal across, time, location and target type (cases, deaths) than scores on the natural scale. Scores on the log scale were much less influenced by the overall incidence level in a country, and showed a slight tendency to be higher in locations with very low incidences. We found that model rankings changed noticeably. 
%, favouring models like epiforecasts-EpiNow2 which uses a log scale generative process and a negative binomial observation model, and disfavouring models like MUNI-ARIMA which uses a square root transform to stabilise variance. 
On the natural scale, missing the peak and overshooting was more severely penalised than missing the nadir and the following upswing in numbers. Both failure modes tended to be more equally penalised on the log scale (with undershooting receiving slightly higher penalties in our example).
